---
title: "MES vs MES"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup}
library(tidyverse)
library(xlsx)
library(DT)
library(gt)
library(webshot2)
```

# Import data from study database .xlsx file

```{r, import xlsx file}
fname <- "FNIH prospective study database excluding follow-up exams.xlsx"
```

```{r}
q1 <- xlsx::read.xlsx2(file = fname, startRow = 3, sheetName = "Worksheet (2)")


q1 <- q1 |> 
  select(contains("MES"), MUSIC_ID) |> 
  mutate(
    across(contains("MES"), as.integer)
  ) |> 
  drop_na()
  
q1_na <- q1 |> 
  select(contains("MES"))

datatable(q1)
datatable(q1_na)
```

#MES in REctum vs MES
```{r}
df_MES <- read.xlsx2(fname, sheetName = "MES_vs_MES")
df_MES_re <- df_MES |>
  mutate(
    across(3:26, as.integer)
  ) 
```

select cases where MES_Rectum == 0 vs MES in AC

```{r}
df_MES_re[1,3] <- sum((q1$MES_Rectum == 0) & (q1$MES_Ascending_Colon == 0))
df_MES_re[1,4] <- sum((q1$MES_Rectum == 0) & (q1$MES_Ascending_Colon == 1))
df_MES_re[1,5] <- sum((q1$MES_Rectum == 0) & (q1$MES_Ascending_Colon > 1))

df_MES_re[2,3] <- sum((q1$MES_Rectum == 1) & (q1$MES_Ascending_Colon == 0))
df_MES_re[2,4] <- sum((q1$MES_Rectum == 1) & (q1$MES_Ascending_Colon == 1))
df_MES_re[2,5] <- sum((q1$MES_Rectum == 1) & (q1$MES_Ascending_Colon > 1))

df_MES_re[3,3] <- sum((q1$MES_Rectum > 1) & (q1$MES_Ascending_Colon == 0))
df_MES_re[3,4] <- sum((q1$MES_Rectum > 1) & (q1$MES_Ascending_Colon == 1))
df_MES_re[3,5] <- sum((q1$MES_Rectum > 1) & (q1$MES_Ascending_Colon > 1))
```


select cases where MES_Rectum == 0 vs MES in TC

```{r}
df_MES_re[1,6] <- sum((q1$MES_Rectum == 0) & (q1$MES_Transverse_Colon == 0))
df_MES_re[1,7] <- sum((q1$MES_Rectum == 0) & (q1$MES_Transverse_Colon == 1))
df_MES_re[1,8] <- sum((q1$MES_Rectum == 0) & (q1$MES_Transverse_Colon > 1))

df_MES_re[2,6] <- sum((q1$MES_Rectum == 1) & (q1$MES_Transverse_Colon == 0))
df_MES_re[2,7] <- sum((q1$MES_Rectum == 1) & (q1$MES_Transverse_Colon == 1))
df_MES_re[2,8] <- sum((q1$MES_Rectum == 1) & (q1$MES_Transverse_Colon > 1))

df_MES_re[3,6] <- sum((q1$MES_Rectum > 1) & (q1$MES_Transverse_Colon == 0))
df_MES_re[3,7] <- sum((q1$MES_Rectum > 1) & (q1$MES_Transverse_Colon == 1))
df_MES_re[3,8] <- sum((q1$MES_Rectum > 1) & (q1$MES_Transverse_Colon > 1))
```

select cases where MES_Rectum == 0 vs MES in DC

```{r}
df_MES_re[1,9] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0))
df_MES_re[1,10] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 1))
df_MES_re[1,11] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon > 1))

df_MES_re[2,9] <- sum((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon == 0))
df_MES_re[2,10] <- sum((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon == 1))
df_MES_re[2,11] <- sum((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon > 1))

df_MES_re[3,9] <- sum((q1$MES_Rectum > 1) & (q1$MES_Descending_Colon == 0))
df_MES_re[3,10] <- sum((q1$MES_Rectum > 1) & (q1$MES_Descending_Colon == 1))
df_MES_re[3,11] <- sum((q1$MES_Rectum > 1) & (q1$MES_Descending_Colon > 1))
```

select cases where MES_Rectum == 0 vs MES in RE

```{r}
df_MES_re[1,12] <- sum((q1$MES_Rectum == 0) & (q1$MES_Rectum == 0))
df_MES_re[1,13] <- sum((q1$MES_Rectum == 0) & (q1$MES_Rectum == 1))
df_MES_re[1,14] <- sum((q1$MES_Rectum == 0) & (q1$MES_Rectum > 1))

df_MES_re[2,12] <- sum((q1$MES_Rectum == 1) & (q1$MES_Rectum == 0))
df_MES_re[2,13] <- sum((q1$MES_Rectum == 1) & (q1$MES_Rectum == 1))
df_MES_re[2,14] <- sum((q1$MES_Rectum == 1) & (q1$MES_Rectum > 1))

df_MES_re[3,12] <- sum((q1$MES_Rectum > 1) & (q1$MES_Rectum == 0))
df_MES_re[3,13] <- sum((q1$MES_Rectum > 1) & (q1$MES_Rectum == 1))
df_MES_re[3,14] <- sum((q1$MES_Rectum > 1) & (q1$MES_Rectum > 1))
```

calculate percentages

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_ac_mes_0 = ac_mes_0 / sum(ac_mes_0, ac_mes_1, ac_mes_.1)) |> 
  mutate(percent_ac_mes_1 = ac_mes_1 / sum(ac_mes_0, ac_mes_1, ac_mes_.1)) |> 
  mutate(percent_ac_mes_.1 = ac_mes_.1 / sum(ac_mes_0, ac_mes_1, ac_mes_.1))

df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_tc_mes_0 = tc_mes_0 / sum(tc_mes_0, tc_mes_1, tc_mes_.1)) |> 
  mutate(percent_tc_mes_1 = tc_mes_1 / sum(tc_mes_0, tc_mes_1, tc_mes_.1)) |> 
  mutate(percent_tc_mes_.1 = tc_mes_.1 / sum(tc_mes_0, tc_mes_1, tc_mes_.1))

df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_dc_mes_0 = dc_mes_0 / sum(dc_mes_0, dc_mes_1, dc_mes_.1)) |> 
  mutate(percent_dc_mes_1 = dc_mes_1 / sum(dc_mes_0, dc_mes_1, dc_mes_.1)) |> 
  mutate(percent_dc_mes_.1 = dc_mes_.1 / sum(dc_mes_0, dc_mes_1, dc_mes_.1))

df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_re_mes_0 = re_mes_0 / sum(re_mes_0, re_mes_1, re_mes_.1)) |> 
  mutate(percent_re_mes_1 = re_mes_1 / sum(re_mes_0, re_mes_1, re_mes_.1)) |> 
  mutate(percent_re_mes_.1 = re_mes_.1 / sum(re_mes_0, re_mes_1, re_mes_.1))
```

Format values as xx.x% (n)

```{r}
df_MES_re <- df_MES_re |> 
  mutate(ac_mes_0_f = paste0(format(round(percent_ac_mes_0 * 100, 1), nsmall = 1), "%\n(", ac_mes_0, ")")) |> 
  mutate(ac_mes_1_f = paste0(format(round(percent_ac_mes_1 * 100, 1), nsmall = 1), "%\n(", ac_mes_1, ")")) |> 
  mutate(ac_mes_.1_f = paste0(format(round(percent_ac_mes_.1 * 100, 1), nsmall = 1), "%\n(", ac_mes_.1, ")")) |> 
  mutate(tc_mes_0_f = paste0(format(round(percent_tc_mes_0 * 100, 1), nsmall = 1), "%\n(", tc_mes_0, ")")) |> 
  mutate(tc_mes_1_f = paste0(format(round(percent_tc_mes_1 * 100, 1), nsmall = 1), "%\n(", tc_mes_1, ")")) |> 
  mutate(tc_mes_.1_f = paste0(format(round(percent_tc_mes_.1 * 100, 1), nsmall = 1), "%\n(", tc_mes_.1, ")")) |> 
  mutate(dc_mes_0_f = paste0(format(round(percent_dc_mes_0 * 100, 1), nsmall = 1), "%\n(", dc_mes_0, ")")) |> 
  mutate(dc_mes_1_f = paste0(format(round(percent_dc_mes_1 * 100, 1), nsmall = 1), "%\n(", dc_mes_1, ")")) |> 
  mutate(dc_mes_.1_f = paste0(format(round(percent_dc_mes_.1 * 100, 1), nsmall = 1), "%\n(", dc_mes_.1, ")")) |> 
  mutate(re_mes_0_f = paste0(format(round(percent_re_mes_0 * 100, 1), nsmall = 1), "%\n(", re_mes_0, ")")) |> 
  mutate(re_mes_1_f = paste0(format(round(percent_re_mes_1 * 100, 1), nsmall = 1), "%\n(", re_mes_1, ")")) |> 
  mutate(re_mes_.1_f = paste0(format(round(percent_re_mes_.1 * 100, 1), nsmall = 1), "%\n(", re_mes_.1, ")"))
```

## MES rectum vs MES AC

```{r}
MES_r_MES_a <- df_MES_re |> 
  select(location, mes_index, ac_mes_0_f:ac_mes_.1_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**MES in Ascending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Ascending Colon",
    columns = starts_with("ac")
  ) |> 
  cols_label(
    ac_mes_0_f = c("0"),
    ac_mes_1_f = c("1"),
    ac_mes_.1_f = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_a
```

## MES rectum vs MES TC

```{r}
MES_r_MES_t <- df_MES_re |> 
  select(location, mes_index, tc_mes_0_f:tc_mes_.1_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**MES in Transverse Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Transverse Colon",
    columns = starts_with("tc")
  ) |> 
  cols_label(
    tc_mes_0_f = c("0"),
    tc_mes_1_f = c("1"),
    tc_mes_.1_f = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_t
```

## MES rectum vs MES DC

```{r}
MES_r_MES_d <- df_MES_re |> 
  select(location, mes_index, dc_mes_0_f:dc_mes_.1_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**MES in Descending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Descending Colon",
    columns = starts_with("dc")
  ) |> 
  cols_label(
    dc_mes_0_f = c("0"),
    dc_mes_1_f = c("1"),
    dc_mes_.1_f = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_d
```

## MES rectum vs MES RE

```{r}
MES_r_MES_r <- df_MES_re |> 
  select(location, mes_index, re_mes_0_f:re_mes_.1_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**MES in Rectum vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Rectum",
    columns = starts_with("re")
  ) |> 
  cols_label(
    re_mes_0_f = c("0"),
    re_mes_1_f = c("1"),
    re_mes_.1_f = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_r
```

#tables with N values only
```{r}
MES_r_MES_a_n <- df_MES_re |> 
  select(location, mes_index, ac_mes_0:ac_mes_.1) |> 
  gt() |> 
  tab_header(
    title = md("**MES in Ascending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Ascending Colon",
    columns = starts_with("ac")
  ) |> 
  cols_label(
    ac_mes_0 = c("0"),
    ac_mes_1 = c("1"),
    ac_mes_.1 = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_t_n <- df_MES_re |> 
  select(location, mes_index, tc_mes_0:tc_mes_.1) |> 
  gt() |> 
  tab_header(
    title = md("**MES in Transverse Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Transverse Colon",
    columns = starts_with("tc")
  ) |> 
  cols_label(
    tc_mes_0 = c("0"),
    tc_mes_1 = c("1"),
    tc_mes_.1 = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_d_n <- df_MES_re |> 
  select(location, mes_index, dc_mes_0:dc_mes_.1) |> 
  gt() |> 
  tab_header(
    title = md("**MES in Descending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Descending Colon",
    columns = starts_with("dc")
  ) |> 
  cols_label(
    dc_mes_0 = c("0"),
    dc_mes_1 = c("1"),
    dc_mes_.1 = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_r_n <- df_MES_re |> 
  select(location, mes_index, re_mes_0:re_mes_.1) |> 
  gt() |> 
  tab_header(
    title = md("**MES in Rectum vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Rectum",
    columns = starts_with("re")
  ) |> 
  cols_label(
    re_mes_0 = c("0"),
    re_mes_1 = c("1"),
    re_mes_.1 = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_MES_a_n
MES_r_MES_t_n
MES_r_MES_d_n
MES_r_MES_r_n
```

#MES in Rectum and Descending Colon vs MES
```{r}
df_MES <- read.xlsx2(fname, sheetName = "MES_vs_MES")
df_MES_rd <- df_MES |>
  mutate(
    across(3:26, as.integer)
  ) |> 
  mutate(location = paste0(location, " and descending colon"))
```

select cases where MES_Rectum & MES_Descending_colon == 0 vs MES in AC

```{r}
df_MES_rd[1,3] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Ascending_Colon == 0))
df_MES_rd[1,4] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Ascending_Colon == 1))
df_MES_rd[1,5] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Ascending_Colon > 1))

df_MES_rd[2,3] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Ascending_Colon == 0)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Ascending_Colon == 0)))
df_MES_rd[2,4] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Ascending_Colon == 1)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Ascending_Colon == 1)))
df_MES_rd[2,5] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Ascending_Colon > 1)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Ascending_Colon > 0)))

df_MES_rd[3,3] <- sum(((q1$MES_Rectum > 1) & (q1$MES_Ascending_Colon == 0)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Ascending_Colon == 0)))
df_MES_rd[3,4] <- sum(((q1$MES_Rectum > 1) & (q1$MES_Ascending_Colon == 1)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Ascending_Colon == 1)))
df_MES_rd[3,5] <- sum(((q1$MES_Rectum > 1) & (q1$MES_Ascending_Colon > 1)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Ascending_Colon > 1)))
```


select cases wherd MES_Rectum & MES_Descending_colon == 0 vs MES in TC

```{r}
df_MES_rd[1,6] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Transverse_Colon == 0))
df_MES_rd[1,7] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Transverse_Colon == 1))
df_MES_rd[1,8] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Transverse_Colon > 1))

df_MES_rd[2,6] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Transverse_Colon == 0)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Transverse_Colon == 0)))
df_MES_rd[2,7] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Transverse_Colon == 1)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Transverse_Colon == 1)))
df_MES_rd[2,8] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Transverse_Colon > 1)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Transverse_Colon > 1)))

df_MES_rd[3,6] <- sum(((q1$MES_Rectum > 1) & (q1$MES_Transverse_Colon == 0)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Transverse_Colon == 0)))
df_MES_rd[3,7] <- sum(((q1$MES_Rectum > 1) & (q1$MES_Transverse_Colon == 1)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Transverse_Colon == 1)))
df_MES_rd[3,8] <- sum(((q1$MES_Rectum > 1) & (q1$MES_Transverse_Colon > 1)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Transverse_Colon > 1)))
```

select cases wherd MES_Rectum & MES_Descending_colon == 0 vs MES in DC

```{r}
df_MES_rd[1,9] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Descending_Colon == 0))
df_MES_rd[1,10] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Descending_Colon == 1))
df_MES_rd[1,11] <- sum((q1$MES_Rectum == 0) & (q1$MES_Descending_Colon == 0) & (q1$MES_Descending_Colon > 1))

df_MES_rd[2,9] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Descending_Colon == 0)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Descending_Colon == 0)))
df_MES_rd[2,10] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Descending_Colon == 1)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Descending_Colon == 1)))
df_MES_rd[2,11] <- sum(((q1$MES_Rectum == 1) & (q1$MES_Descending_Colon <= 1) & (q1$MES_Descending_Colon > 1)) | ((q1$MES_Rectum <= 1) & (q1$MES_Descending_Colon == 1) & (q1$MES_Descending_Colon > 1)))

df_MES_rd[3,9] <- sum(((q1$MES_Rectum > 1) & (q1$MES_Descending_Colon == 0)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Descending_Colon == 0)))
df_MES_rd[3,10] <-sum(((q1$MES_Rectum > 1) & (q1$MES_Descending_Colon == 1)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Descending_Colon == 1)))
df_MES_rd[3,11] <-sum(((q1$MES_Rectum > 1) & (q1$MES_Descending_Colon > 1)) | ((q1$MES_Descending_Colon > 1) & (q1$MES_Descending_Colon > 1)))
```


calculate percentages

```{r}
df_MES_rd <- df_MES_rd |> 
  rowwise() |> 
  mutate(percent_ac_mes_0 = ac_mes_0 / sum(ac_mes_0, ac_mes_1, ac_mes_.1)) |> 
  mutate(percent_ac_mes_1 = ac_mes_1 / sum(ac_mes_0, ac_mes_1, ac_mes_.1)) |> 
  mutate(percent_ac_mes_.1 = ac_mes_.1 / sum(ac_mes_0, ac_mes_1, ac_mes_.1))

df_MES_rd <- df_MES_rd |> 
  rowwise() |> 
  mutate(percent_tc_mes_0 = tc_mes_0 / sum(tc_mes_0, tc_mes_1, tc_mes_.1)) |> 
  mutate(percent_tc_mes_1 = tc_mes_1 / sum(tc_mes_0, tc_mes_1, tc_mes_.1)) |> 
  mutate(percent_tc_mes_.1 = tc_mes_.1 / sum(tc_mes_0, tc_mes_1, tc_mes_.1))

df_MES_rd <- df_MES_rd |> 
  rowwise() |> 
  mutate(percent_dc_mes_0 = dc_mes_0 / sum(dc_mes_0, dc_mes_1, dc_mes_.1)) |> 
  mutate(percent_dc_mes_1 = dc_mes_1 / sum(dc_mes_0, dc_mes_1, dc_mes_.1)) |> 
  mutate(percent_dc_mes_.1 = dc_mes_.1 / sum(dc_mes_0, dc_mes_1, dc_mes_.1))
```

Format values as xx.x% (n)

```{r}
df_MES_rd <- df_MES_rd |> 
  mutate(ac_mes_0_f = paste0(format(round(percent_ac_mes_0 * 100, 1), nsmall = 1), "%\n(", ac_mes_0, ")")) |> 
  mutate(ac_mes_1_f = paste0(format(round(percent_ac_mes_1 * 100, 1), nsmall = 1), "%\n(", ac_mes_1, ")")) |> 
  mutate(ac_mes_.1_f = paste0(format(round(percent_ac_mes_.1 * 100, 1), nsmall = 1), "%\n(", ac_mes_.1, ")")) |> 
  mutate(tc_mes_0_f = paste0(format(round(percent_tc_mes_0 * 100, 1), nsmall = 1), "%\n(", tc_mes_0, ")")) |> 
  mutate(tc_mes_1_f = paste0(format(round(percent_tc_mes_1 * 100, 1), nsmall = 1), "%\n(", tc_mes_1, ")")) |> 
  mutate(tc_mes_.1_f = paste0(format(round(percent_tc_mes_.1 * 100, 1), nsmall = 1), "%\n(", tc_mes_.1, ")")) |> 
  mutate(dc_mes_0_f = paste0(format(round(percent_dc_mes_0 * 100, 1), nsmall = 1), "%\n(", dc_mes_0, ")")) |> 
  mutate(dc_mes_1_f = paste0(format(round(percent_dc_mes_1 * 100, 1), nsmall = 1), "%\n(", dc_mes_1, ")")) |> 
  mutate(dc_mes_.1_f = paste0(format(round(percent_dc_mes_.1 * 100, 1), nsmall = 1), "%\n(", dc_mes_.1, ")"))
```

## MES rectum and Descending Colon vs MES AC

```{r}
MES_rd_MES_a <- df_MES_rd |> 
  select(location, mes_index, ac_mes_0_f:ac_mes_.1_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**MES in Ascending Colon vs MES in Rectum and Descending Colon**")
  ) |> 
  tab_spanner(
    label = "MES in Ascending Colon",
    columns = starts_with("ac")
  ) |> 
  cols_label(
    ac_mes_0_f = c("0"),
    ac_mes_1_f = c("1"),
    ac_mes_.1_f = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_rd_MES_a
```

## MES rectum and Descending Colon vs MES TC

```{r}
MES_rd_MES_t <- df_MES_rd |> 
  select(location, mes_index, tc_mes_0_f:tc_mes_.1_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**MES in Transverse Colon vs MES in Rectum and Descending Colon**")
  ) |> 
  tab_spanner(
    label = "MES in Transverse Colon",
    columns = starts_with("tc")
  ) |> 
  cols_label(
    tc_mes_0_f = c("0"),
    tc_mes_1_f = c("1"),
    tc_mes_.1_f = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_rd_MES_t
```

## MES rectum and Descending Colon vs MES DC

```{r}
MES_rd_MES_d <- df_MES_rd |> 
  select(location, mes_index, dc_mes_0_f:dc_mes_.1_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**MES in Descending Colon vs MES in Rectum and Descending Colon**")
  ) |> 
  tab_spanner(
    label = "MES in Descending Colon",
    columns = starts_with("dc")
  ) |> 
  cols_label(
    dc_mes_0_f = c("0"),
    dc_mes_1_f = c("1"),
    dc_mes_.1_f = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_rd_MES_d
```



#tables with N values only
```{r}
MES_rd_MES_a_n <- df_MES_rd |> 
  select(location, mes_index, ac_mes_0:ac_mes_.1) |> 
  gt() |> 
  tab_header(
    title = md("**MES in Ascending Colon vs MES in Rectum and Descending Colon**")
  ) |> 
  tab_spanner(
    label = "MES in Ascending Colon",
    columns = starts_with("ac")
  ) |> 
  cols_label(
    ac_mes_0 = c("0"),
    ac_mes_1 = c("1"),
    ac_mes_.1 = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_rd_MES_t_n <- df_MES_rd |> 
  select(location, mes_index, tc_mes_0:tc_mes_.1) |> 
  gt() |> 
  tab_header(
    title = md("**MES in Transverse Colon vs MES in Rectum and Descending Colon**")
  ) |> 
  tab_spanner(
    label = "MES in Transverse Colon",
    columns = starts_with("tc")
  ) |> 
  cols_label(
    tc_mes_0 = c("0"),
    tc_mes_1 = c("1"),
    tc_mes_.1 = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_rd_MES_d_n <- df_MES_rd |> 
  select(location, mes_index, dc_mes_0:dc_mes_.1) |> 
  gt() |> 
  tab_header(
    title = md("**MES in Descending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "MES in Descending Colon",
    columns = starts_with("dc")
  ) |> 
  cols_label(
    dc_mes_0 = c("0"),
    dc_mes_1 = c("1"),
    dc_mes_.1 = "> 1",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )



MES_rd_MES_a_n
MES_rd_MES_t_n
MES_rd_MES_d_n
```

#Export N values
```{r, eval=FALSE}
MES_r_MES_a_n |> 
  gtsave(filename = "output_tables/mes_r_mes_a_n.docx")
MES_r_MES_t_n |> 
  gtsave(filename = "output_tables/mes_r_mes_t_n.docx")
MES_r_MES_d_n |> 
  gtsave(filename = "output_tables/mes_r_mes_d_n.docx")
MES_r_MES_r_n |> 
  gtsave(filename = "output_tables/mes_r_mes_r_n.docx")

MES_rd_MES_a_n |> 
  gtsave(filename = "output_tables/mes_rd_mes_a_n.docx")
MES_rd_MES_t_n |> 
  gtsave(filename = "output_tables/mes_rd_mes_t_n.docx")
MES_rd_MES_d_n |> 
  gtsave(filename = "output_tables/mes_rd_mes_d_n.docx")
```