---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup}
library(tidyverse)
library(xlsx)
library(DT)
library(gt)
library(webshot2)
```

# Import data from study database .xlsx file

```{r, import xlsx file}
fname <- "FNIH prospective study database excluding follow-up exams.xlsx"
```

```{r}
q1 <- xlsx::read.xlsx2(file = fname, 2, startRow = 3, endRow = 169)

q1 <- q1 |> 
  select(MES_Rectum, contains("NHI_max")) |> 
  mutate(
    across(contains("NHI_max"), as.integer)
  ) |> 
  mutate(
    across(contains("MES_Rectum"), as.integer) 
  ) |> 
  drop_na()

datatable(q1)
```

# MES in Rectum vs Max NHI

```{r}
df_MES <- read.xlsx2(fname, sheetName = "MES_vs_NHI")
df_MES_re <- df_MES |> 
  mutate(
    across(3:42, as.integer)
  )
```

select cases where MES_Rectum == 0 vs max NHI in AC

```{r}
df_MES_re[1,3] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_AC == 0))
df_MES_re[1,4] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_AC == 1))
df_MES_re[1,5] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_AC == 2))
df_MES_re[1,6] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_AC == 3))
df_MES_re[1,7] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_AC == 4))

df_MES_re[2,3] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_AC == 0))
df_MES_re[2,4] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_AC == 1))
df_MES_re[2,5] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_AC == 2))
df_MES_re[2,6] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_AC == 3))
df_MES_re[2,7] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_AC == 4))

df_MES_re[3,3] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_AC == 0))
df_MES_re[3,4] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_AC == 1))
df_MES_re[3,5] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_AC == 2))
df_MES_re[3,6] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_AC == 3))
df_MES_re[3,7] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_AC == 4))
```


select cases where MES_Rectum == 0 vs max NHI in TC

```{r}
df_MES_re[1,8] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_TC == 0))
df_MES_re[1,9] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_TC == 1))
df_MES_re[1,10] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_TC == 2))
df_MES_re[1,11] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_TC == 3))
df_MES_re[1,12] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_TC == 4))

df_MES_re[2,8] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_TC == 0))
df_MES_re[2,9] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_TC == 1))
df_MES_re[2,10] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_TC == 2))
df_MES_re[2,11] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_TC == 3))
df_MES_re[2,12] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_TC == 4))

df_MES_re[3,8] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_TC == 0))
df_MES_re[3,9] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_TC == 1))
df_MES_re[3,10] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_TC == 2))
df_MES_re[3,11] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_TC == 3))
df_MES_re[3,12] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_TC == 4))
```

select cases where MES_Rectum == 0 vs max NHI in DC

```{r}
df_MES_re[1,13] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_DC == 0))
df_MES_re[1,14] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_DC == 1))
df_MES_re[1,15] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_DC == 2))
df_MES_re[1,16] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_DC == 3))
df_MES_re[1,17] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_DC == 4))

df_MES_re[2,13] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_DC == 0))
df_MES_re[2,14] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_DC == 1))
df_MES_re[2,15] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_DC == 2))
df_MES_re[2,16] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_DC == 3))
df_MES_re[2,17] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_DC == 4))

df_MES_re[3,13] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_DC == 0))
df_MES_re[3,14] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_DC == 1))
df_MES_re[3,15] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_DC == 2))
df_MES_re[3,16] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_DC == 3))
df_MES_re[3,17] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_DC == 4))
```

select cases where MES_Rectum == 0 vs max NHI in RE

```{r}
df_MES_re[1,18] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_RE == 0))
df_MES_re[1,19] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_RE == 1))
df_MES_re[1,20] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_RE == 2))
df_MES_re[1,21] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_RE == 3))
df_MES_re[1,22] <- sum((q1$MES_Rectum == 0) & (q1$NHI_max_RE == 4))

df_MES_re[2,18] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_RE == 0))
df_MES_re[2,19] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_RE == 1))
df_MES_re[2,20] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_RE == 2))
df_MES_re[2,21] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_RE == 3))
df_MES_re[2,22] <- sum((q1$MES_Rectum == 1) & (q1$NHI_max_RE == 4))

df_MES_re[3,18] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_RE == 0))
df_MES_re[3,19] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_RE == 1))
df_MES_re[3,20] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_RE == 2))
df_MES_re[3,21] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_RE == 3))
df_MES_re[3,22] <- sum((q1$MES_Rectum > 1) & (q1$NHI_max_RE == 4))
```

calculate percentages

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_ac_nhi_0 = max_ac_nhi_0 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_1 = max_ac_nhi_1 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_2 = max_ac_nhi_2 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_3 = max_ac_nhi_3 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_4 = max_ac_nhi_4 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4))
```

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_tc_nhi_0 = max_tc_nhi_0 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_1 = max_tc_nhi_1 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_2 = max_tc_nhi_2 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_3 = max_tc_nhi_3 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_4 = max_tc_nhi_4 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4))
```

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_dc_nhi_0 = max_dc_nhi_0 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_1 = max_dc_nhi_1 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_2 = max_dc_nhi_2 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_3 = max_dc_nhi_3 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_4 = max_dc_nhi_4 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4))
```

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_re_nhi_0 = max_re_nhi_0 / sum(max_re_nhi_0, max_re_nhi_1, max_re_nhi_2, max_re_nhi_3, max_re_nhi_4)) |> 
  mutate(percent_max_re_nhi_1 = max_re_nhi_1 / sum(max_re_nhi_0, max_re_nhi_1, max_re_nhi_2, max_re_nhi_3, max_re_nhi_4)) |> 
  mutate(percent_max_re_nhi_2 = max_re_nhi_2 / sum(max_re_nhi_0, max_re_nhi_1, max_re_nhi_2, max_re_nhi_3, max_re_nhi_4)) |> 
  mutate(percent_max_re_nhi_3 = max_re_nhi_3 / sum(max_re_nhi_0, max_re_nhi_1, max_re_nhi_2, max_re_nhi_3, max_re_nhi_4)) |> 
  mutate(percent_max_re_nhi_4 = max_re_nhi_4 / sum(max_re_nhi_0, max_re_nhi_1, max_re_nhi_2, max_re_nhi_3, max_re_nhi_4))
```

Format values as xx.x% (n)

```{r}
df_MES_re <- df_MES_re |> 
  mutate(max_ac_nhi_0_f = paste0(format(round(percent_max_ac_nhi_0 * 100, 1), nsmall = 1), "%\n(", max_ac_nhi_0, ")")) |> 
  mutate(max_ac_nhi_1_f = paste0(format(round(percent_max_ac_nhi_1 * 100, 1), nsmall = 1), "%\n(", max_ac_nhi_1, ")")) |> 
  mutate(max_ac_nhi_2_f = paste0(format(round(percent_max_ac_nhi_2 * 100, 1), nsmall = 1), "%\n(", max_ac_nhi_2, ")")) |> 
  mutate(max_ac_nhi_3_f = paste0(format(round(percent_max_ac_nhi_3 * 100, 1), nsmall = 1), "%\n(", max_ac_nhi_3, ")")) |> 
  mutate(max_ac_nhi_4_f = paste0(format(round(percent_max_ac_nhi_4 * 100, 1), nsmall = 1), "%\n(", max_ac_nhi_4, ")")) |> 
  mutate(max_tc_nhi_0_f = paste0(format(round(percent_max_tc_nhi_0 * 100, 1), nsmall = 1), "%\n(", max_tc_nhi_0, ")")) |> 
  mutate(max_tc_nhi_1_f = paste0(format(round(percent_max_tc_nhi_1 * 100, 1), nsmall = 1), "%\n(", max_tc_nhi_1, ")")) |> 
  mutate(max_tc_nhi_2_f = paste0(format(round(percent_max_tc_nhi_2 * 100, 1), nsmall = 1), "%\n(", max_tc_nhi_2, ")")) |> 
  mutate(max_tc_nhi_3_f = paste0(format(round(percent_max_tc_nhi_3 * 100, 1), nsmall = 1), "%\n(", max_tc_nhi_3, ")")) |> 
  mutate(max_tc_nhi_4_f = paste0(format(round(percent_max_tc_nhi_4 * 100, 1), nsmall = 1), "%\n(", max_tc_nhi_4, ")")) |> 
  mutate(max_dc_nhi_0_f = paste0(format(round(percent_max_dc_nhi_0 * 100, 1), nsmall = 1), "%\n(", max_dc_nhi_0, ")")) |> 
  mutate(max_dc_nhi_1_f = paste0(format(round(percent_max_dc_nhi_1 * 100, 1), nsmall = 1), "%\n(", max_dc_nhi_1, ")")) |> 
  mutate(max_dc_nhi_2_f = paste0(format(round(percent_max_dc_nhi_2 * 100, 1), nsmall = 1), "%\n(", max_dc_nhi_2, ")")) |> 
  mutate(max_dc_nhi_3_f = paste0(format(round(percent_max_dc_nhi_3 * 100, 1), nsmall = 1), "%\n(", max_dc_nhi_3, ")")) |> 
  mutate(max_dc_nhi_4_f = paste0(format(round(percent_max_dc_nhi_4 * 100, 1), nsmall = 1), "%\n(", max_dc_nhi_4, ")")) |> 
  mutate(max_re_nhi_0_f = paste0(format(round(percent_max_re_nhi_0 * 100, 1), nsmall = 1), "%\n(", max_re_nhi_0, ")")) |> 
  mutate(max_re_nhi_1_f = paste0(format(round(percent_max_re_nhi_1 * 100, 1), nsmall = 1), "%\n(", max_re_nhi_1, ")")) |> 
  mutate(max_re_nhi_2_f = paste0(format(round(percent_max_re_nhi_2 * 100, 1), nsmall = 1), "%\n(", max_re_nhi_2, ")")) |> 
  mutate(max_re_nhi_3_f = paste0(format(round(percent_max_re_nhi_3 * 100, 1), nsmall = 1), "%\n(", max_re_nhi_3, ")")) |> 
  mutate(max_re_nhi_4_f = paste0(format(round(percent_max_re_nhi_4 * 100, 1), nsmall = 1), "%\n(", max_re_nhi_4, ")"))
```

## MES rectum vs NHI AC

```{r}
MES_r_NHI_a <- df_MES_re |> 
  select(location, mes_index, max_ac_nhi_0_f:max_ac_nhi_4_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max NHI in Ascending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Ascending Colon",
    columns = starts_with("max_ac")
  ) |> 
  cols_label(
    max_ac_nhi_0_f = 0,
    max_ac_nhi_1_f = 1,
    max_ac_nhi_2_f = 2,
    max_ac_nhi_3_f = 3,
    max_ac_nhi_4_f = 4,
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_NHI_a
```

## MES rectum vs NHI TC

```{r}
MES_r_NHI_t <- df_MES_re |> 
  select(location, mes_index, max_tc_nhi_0_f:max_tc_nhi_4_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max NHI in Transverse Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Transverse Colon",
    columns = starts_with("max_tc")
  ) |> 
  cols_label(
    max_tc_nhi_0_f = 0,
    max_tc_nhi_1_f = 1,
    max_tc_nhi_2_f = 2,
    max_tc_nhi_3_f = 3,
    max_tc_nhi_4_f = 4,
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_NHI_t
```

## MES rectum vs NHI DC

```{r}
MES_r_NHI_d <- df_MES_re |> 
  select(location, mes_index, max_dc_nhi_0_f:max_dc_nhi_4_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max NHI in Descending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Descending Colon",
    columns = starts_with("max_dc")
  ) |> 
  cols_label(
    max_dc_nhi_0_f = 0,
    max_dc_nhi_1_f = 1,
    max_dc_nhi_2_f = 2,
    max_dc_nhi_3_f = 3,
    max_dc_nhi_4_f = 4,
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_NHI_d
```

## MES rectum vs NHI RE

```{r}
MES_r_NHI_r <- df_MES_re |> 
  select(location, mes_index, max_re_nhi_0_f:max_re_nhi_4_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max NHI in Rectum Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Rectum Colon",
    columns = starts_with("max_re")
  ) |> 
  cols_label(
    max_re_nhi_0_f = 0,
    max_re_nhi_1_f = 1,
    max_re_nhi_2_f = 2,
    max_re_nhi_3_f = 3,
    max_re_nhi_4_f = 4,
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_NHI_r
```

```{r, eval= FALSE}
MES_r_NHI_a |> 
  gtsave(filename = "output_tables/mes_r_nhi_a.png")

MES_r_NHI_t |> 
  gtsave(filename = "output_tables/mes_r_nhi_t.png")

MES_r_NHI_d |> 
  gtsave(filename = "output_tables/mes_r_nhi_d.png")

MES_r_NHI_r |> 
  gtsave(filename = "output_tables/mes_r_nhi_r.png")
```

```{r, eval= FALSE}
MES_r_NHI_a |> 
  gtsave(filename = "output_tables/mes_r_nhi_a.html")

MES_r_NHI_t |> 
  gtsave(filename = "output_tables/mes_r_nhi_t.html")

MES_r_NHI_d |> 
  gtsave(filename = "output_tables/mes_r_nhi_d.html")

MES_r_NHI_r |> 
  gtsave(filename = "output_tables/mes_r_nhi_r.html")
```

