---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup}
library(tidyverse)
library(xlsx)
library(DT)
library(gt)
library(glue)
library(htmlwidgets)
library(webshot2)
```

# Import data from study database .xlsx file

```{r, import xlsx file}
fname <- "FNIH prospective study database excluding follow-up exams.xlsx"
```

```{r}
q1 <- xlsx::read.xlsx2(file = fname, 2, startRow = 3, endRow = 169)
datatable(q1)
 
q2 <- xlsx::read.xlsx2(file = fname, 4, startRow = 3)
datatable(q2)
```

Count number of cases grouped by their highest MES score in the rectum
```{r}
q2[1,3] <- sum(q1$MES_Rectum == 0)
q2[2,3] <- sum(q1$MES_Rectum == 1)
q2[3,3] <- sum(q1$MES_Rectum == 2)
q2[4,3] <- sum(q1$MES_Rectum == 3)

```

Proportion of biopsies with histologic score based on maximum NHI at AC
```{r}
q2[1,4] <- sum((q1$NHI_max_AC == 0) & (q1$MES_Rectum == 0))
q2[2,4] <- sum((q1$NHI_max_AC == 0) & (q1$MES_Rectum == 1))
q2[3,4] <- sum((q1$NHI_max_AC == 0) & (q1$MES_Rectum == 2))
q2[4,4] <- sum((q1$NHI_max_AC == 0) & (q1$MES_Rectum == 3))

q2[1,5] <- sum((q1$NHI_max_AC == 1) & (q1$MES_Rectum == 0))
q2[2,5] <- sum((q1$NHI_max_AC == 1) & (q1$MES_Rectum == 1))
q2[3,5] <- sum((q1$NHI_max_AC == 1) & (q1$MES_Rectum == 2))
q2[4,5] <- sum((q1$NHI_max_AC == 1) & (q1$MES_Rectum == 3))

q2[1,6] <- sum((q1$NHI_max_AC == 2) & (q1$MES_Rectum == 0))
q2[2,6] <- sum((q1$NHI_max_AC == 2) & (q1$MES_Rectum == 1))
q2[3,6] <- sum((q1$NHI_max_AC == 2) & (q1$MES_Rectum == 2))
q2[4,6] <- sum((q1$NHI_max_AC == 2) & (q1$MES_Rectum == 3))

q2[1,7] <- sum((q1$NHI_max_AC == 3) & (q1$MES_Rectum == 0))
q2[2,7] <- sum((q1$NHI_max_AC == 3) & (q1$MES_Rectum == 1))
q2[3,7] <- sum((q1$NHI_max_AC == 3) & (q1$MES_Rectum == 2))
q2[4,7] <- sum((q1$NHI_max_AC == 3) & (q1$MES_Rectum == 3))

q2[1,8] <- sum((q1$NHI_max_AC == 4) & (q1$MES_Rectum == 0))
q2[2,8] <- sum((q1$NHI_max_AC == 4) & (q1$MES_Rectum == 1))
q2[3,8] <- sum((q1$NHI_max_AC == 4) & (q1$MES_Rectum == 2))
q2[4,8] <- sum((q1$NHI_max_AC == 4) & (q1$MES_Rectum == 3))
```

Proportion of biopsies with histologic score based on maximum NHI at TC
```{r}
q2[1,9] <- sum((q1$NHI_max_TC == 0) & (q1$MES_Rectum == 0))
q2[2,9] <- sum((q1$NHI_max_TC == 0) & (q1$MES_Rectum == 1))
q2[3,9] <- sum((q1$NHI_max_TC == 0) & (q1$MES_Rectum == 2))
q2[4,9] <- sum((q1$NHI_max_TC == 0) & (q1$MES_Rectum == 3))

q2[1,10] <- sum((q1$NHI_max_TC == 1) & (q1$MES_Rectum == 0))
q2[2,10] <- sum((q1$NHI_max_TC == 1) & (q1$MES_Rectum == 1))
q2[3,10] <- sum((q1$NHI_max_TC == 1) & (q1$MES_Rectum == 2))
q2[4,10] <- sum((q1$NHI_max_TC == 1) & (q1$MES_Rectum == 3))

q2[1,11] <- sum((q1$NHI_max_TC == 2) & (q1$MES_Rectum == 0))
q2[2,11] <- sum((q1$NHI_max_TC == 2) & (q1$MES_Rectum == 1))
q2[3,11] <- sum((q1$NHI_max_TC == 2) & (q1$MES_Rectum == 2))
q2[4,11] <- sum((q1$NHI_max_TC == 2) & (q1$MES_Rectum == 3))

q2[1,12] <- sum((q1$NHI_max_TC == 3) & (q1$MES_Rectum == 0))
q2[2,12] <- sum((q1$NHI_max_TC == 3) & (q1$MES_Rectum == 1))
q2[3,12] <- sum((q1$NHI_max_TC == 3) & (q1$MES_Rectum == 2))
q2[4,12] <- sum((q1$NHI_max_TC == 3) & (q1$MES_Rectum == 3))

q2[1,13] <- sum((q1$NHI_max_TC == 4) & (q1$MES_Rectum == 0))
q2[2,13] <- sum((q1$NHI_max_TC == 4) & (q1$MES_Rectum == 1))
q2[3,13] <- sum((q1$NHI_max_TC == 4) & (q1$MES_Rectum == 2))
q2[4,13] <- sum((q1$NHI_max_TC == 4) & (q1$MES_Rectum == 3))
```

Proportion of biopsies with histologic score based on maximum NHI at DC
```{r}
q2[1,14] <- sum((q1$NHI_max_DC == 0) & (q1$MES_Rectum == 0))
q2[2,14] <- sum((q1$NHI_max_DC == 0) & (q1$MES_Rectum == 1))
q2[3,14] <- sum((q1$NHI_max_DC == 0) & (q1$MES_Rectum == 2))
q2[4,14] <- sum((q1$NHI_max_DC == 0) & (q1$MES_Rectum == 3))

q2[1,15] <- sum((q1$NHI_max_DC == 1) & (q1$MES_Rectum == 0))
q2[2,15] <- sum((q1$NHI_max_DC == 1) & (q1$MES_Rectum == 1))
q2[3,15] <- sum((q1$NHI_max_DC == 1) & (q1$MES_Rectum == 2))
q2[4,15] <- sum((q1$NHI_max_DC == 1) & (q1$MES_Rectum == 3))

q2[1,16] <- sum((q1$NHI_max_DC == 2) & (q1$MES_Rectum == 0))
q2[2,16] <- sum((q1$NHI_max_DC == 2) & (q1$MES_Rectum == 1))
q2[3,16] <- sum((q1$NHI_max_DC == 2) & (q1$MES_Rectum == 2))
q2[4,16] <- sum((q1$NHI_max_DC == 2) & (q1$MES_Rectum == 3))

q2[1,17] <- sum((q1$NHI_max_DC == 3) & (q1$MES_Rectum == 0))
q2[2,17] <- sum((q1$NHI_max_DC == 3) & (q1$MES_Rectum == 1))
q2[3,17] <- sum((q1$NHI_max_DC == 3) & (q1$MES_Rectum == 2))
q2[4,17] <- sum((q1$NHI_max_DC == 3) & (q1$MES_Rectum == 3))

q2[1,18] <- sum((q1$NHI_max_DC == 4) & (q1$MES_Rectum == 0))
q2[2,18] <- sum((q1$NHI_max_DC == 4) & (q1$MES_Rectum == 1))
q2[3,18] <- sum((q1$NHI_max_DC == 4) & (q1$MES_Rectum == 2))
q2[4,18] <- sum((q1$NHI_max_DC == 4) & (q1$MES_Rectum == 3))
```

Proportion of biopsies with histologic score based on maximum NHI at RE
```{r}
q2[1,19] <- sum((q1$NHI_max_RE == 0) & (q1$MES_Rectum == 0))
q2[2,19] <- sum((q1$NHI_max_RE == 0) & (q1$MES_Rectum == 1))
q2[3,19] <- sum((q1$NHI_max_RE == 0) & (q1$MES_Rectum == 2))
q2[4,19] <- sum((q1$NHI_max_RE == 0) & (q1$MES_Rectum == 3))

q2[1,20] <- sum((q1$NHI_max_RE == 1) & (q1$MES_Rectum == 0))
q2[2,20] <- sum((q1$NHI_max_RE == 1) & (q1$MES_Rectum == 1))
q2[3,20] <- sum((q1$NHI_max_RE == 1) & (q1$MES_Rectum == 2))
q2[4,20] <- sum((q1$NHI_max_RE == 1) & (q1$MES_Rectum == 3))

q2[1,21] <- sum((q1$NHI_max_RE == 2) & (q1$MES_Rectum == 0))
q2[2,21] <- sum((q1$NHI_max_RE == 2) & (q1$MES_Rectum == 1))
q2[3,21] <- sum((q1$NHI_max_RE == 2) & (q1$MES_Rectum == 2))
q2[4,21] <- sum((q1$NHI_max_RE == 2) & (q1$MES_Rectum == 3))

q2[1,22] <- sum((q1$NHI_max_RE == 3) & (q1$MES_Rectum == 0))
q2[2,22] <- sum((q1$NHI_max_RE == 3) & (q1$MES_Rectum == 1))
q2[3,22] <- sum((q1$NHI_max_RE == 3) & (q1$MES_Rectum == 2))
q2[4,22] <- sum((q1$NHI_max_RE == 3) & (q1$MES_Rectum == 3))

q2[1,23] <- sum((q1$NHI_max_RE == 4) & (q1$MES_Rectum == 0))
q2[2,23] <- sum((q1$NHI_max_RE == 4) & (q1$MES_Rectum == 1))
q2[3,23] <- sum((q1$NHI_max_RE == 4) & (q1$MES_Rectum == 2))
q2[4,23] <- sum((q1$NHI_max_RE == 4) & (q1$MES_Rectum == 3))
```

```{r}
gt(q2)
```


```{r}
# write.xlsx2(q2, fname, sheetName = "R calc", append = TRUE)
```

# Max NHI in Rectum vs Max NHI
```{r}
df_NHI <- read.xlsx2(fname, sheetName = "NHI_vs_NHI")
df_NHI <- df_NHI |> 
  mutate(
    across(3:32, as.integer)
  )
```

```{r}
df_NHI[1,3] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_AC == 0))
df_NHI[1,4] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_AC == 1))
df_NHI[1,5] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_AC == 2))
df_NHI[1,6] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_AC == 3))
df_NHI[1,7] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_AC == 4))

df_NHI[2,3] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_AC == 0))
df_NHI[2,4] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_AC == 1))
df_NHI[2,5] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_AC == 2))
df_NHI[2,6] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_AC == 3))
df_NHI[2,7] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_AC == 4))

df_NHI[3,3] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_AC == 0))
df_NHI[3,4] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_AC == 1))
df_NHI[3,5] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_AC == 2))
df_NHI[3,6] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_AC == 3))
df_NHI[3,7] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_AC == 4))
```

```{r}
df_NHI[1,8] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_TC == 0))
df_NHI[1,9] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_TC == 1))
df_NHI[1,10] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_TC == 2))
df_NHI[1,11] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_TC == 3))
df_NHI[1,12] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_TC == 4))

df_NHI[2,8] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_TC == 0))
df_NHI[2,9] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_TC == 1))
df_NHI[2,10] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_TC == 2))
df_NHI[2,11] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_TC == 3))
df_NHI[2,12] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_TC == 4))

df_NHI[3,8] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_TC == 0))
df_NHI[3,9] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_TC == 1))
df_NHI[3,10] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_TC == 2))
df_NHI[3,11] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_TC == 3))
df_NHI[3,12] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_TC == 4))
```

```{r}
df_NHI[1,13] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_DC == 0))
df_NHI[1,14] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_DC == 1))
df_NHI[1,15] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_DC == 2))
df_NHI[1,16] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_DC == 3))
df_NHI[1,17] <- sum((q1$NHI_max_RE == 0) & (q1$NHI_max_DC == 4))

df_NHI[2,13] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_DC == 0))
df_NHI[2,14] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_DC == 1))
df_NHI[2,15] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_DC == 2))
df_NHI[2,16] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_DC == 3))
df_NHI[2,17] <- sum((q1$NHI_max_RE == 1) & (q1$NHI_max_DC == 4))

df_NHI[3,13] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_DC == 0))
df_NHI[3,14] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_DC == 1))
df_NHI[3,15] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_DC == 2))
df_NHI[3,16] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_DC == 3))
df_NHI[3,17] <- sum((q1$NHI_max_RE > 1) & (q1$NHI_max_DC == 4))
```

```{r}
df_NHI <- df_NHI |> 
  rowwise() |> 
  mutate(percent_max_ac_nhi_0 = max_ac_nhi_0 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_1 = max_ac_nhi_1 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_2 = max_ac_nhi_2 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_3 = max_ac_nhi_3 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4)) |> 
  mutate(percent_max_ac_nhi_4 = max_ac_nhi_4 / sum(max_ac_nhi_0, max_ac_nhi_1, max_ac_nhi_2, max_ac_nhi_3, max_ac_nhi_4))
```

```{r}
df_NHI <- df_NHI |> 
  rowwise() |> 
  mutate(percent_max_tc_nhi_0 = max_tc_nhi_0 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_1 = max_tc_nhi_1 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_2 = max_tc_nhi_2 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_3 = max_tc_nhi_3 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4)) |> 
  mutate(percent_max_tc_nhi_4 = max_tc_nhi_4 / sum(max_tc_nhi_0, max_tc_nhi_1, max_tc_nhi_2, max_tc_nhi_3, max_tc_nhi_4))
```

```{r}
df_NHI <- df_NHI |> 
  rowwise() |> 
  mutate(percent_max_dc_nhi_0 = max_dc_nhi_0 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_1 = max_dc_nhi_1 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_2 = max_dc_nhi_2 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_3 = max_dc_nhi_3 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4)) |> 
  mutate(percent_max_dc_nhi_4 = max_dc_nhi_4 / sum(max_dc_nhi_0, max_dc_nhi_1, max_dc_nhi_2, max_dc_nhi_3, max_dc_nhi_4))
```

# NHI rectum vs AC
```{r}
NHI_rec_ac_per <- df_NHI |> 
  select(location, nhi_index, percent_max_ac_nhi_0:percent_max_ac_nhi_4) |> 
  gt() |> 
  fmt_percent() |> 
  tab_header(
    title = md("**Max NHI in Ascending Colon vs Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Ascending Colon",
    columns = starts_with("percent")
  ) |> 
  cols_label(
    percent_max_ac_nhi_0 = 0,
    percent_max_ac_nhi_1 = 1,
    percent_max_ac_nhi_2 = 2,
    percent_max_ac_nhi_3 = 3,
    percent_max_ac_nhi_4 = 4,
    nhi_index = "NHI"
  ) |> 
  data_color(
    columns = 3:7,
    method = "numeric",
    palette = c("white", "green"),
    domain = c(0,1)
  )

NHI_rec_ac <- df_NHI |> 
  select(location, nhi_index, max_ac_nhi_0:max_ac_nhi_4) |> 
  gt() |> 
  tab_header(
    title = md("**Max NHI in Ascending Colon vs Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Ascending Colon",
    columns = starts_with("max")
  ) |> 
  cols_label(
    max_ac_nhi_0 = 0,
    max_ac_nhi_1 = 1,
    max_ac_nhi_2 = 2,
    max_ac_nhi_3 = 3,
    max_ac_nhi_4 = 4,
    nhi_index = "NHI"
  )
```

# NHI rectum vs TC
```{r}
NHI_rec_tc_per <- df_NHI |> 
  select(location, nhi_index, percent_max_tc_nhi_0:percent_max_tc_nhi_4) |> 
  gt() |> 
  fmt_percent() |> 
  tab_header(
    title = md("**Max NHI in Transvere Colon vs Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Transverse Colon",
    columns = starts_with("percent")
  ) |> 
  cols_label(
    percent_max_tc_nhi_0 = 0,
    percent_max_tc_nhi_1 = 1,
    percent_max_tc_nhi_2 = 2,
    percent_max_tc_nhi_3 = 3,
    percent_max_tc_nhi_4 = 4,
    nhi_index = "NHI"
  ) |> 
  data_color(
    columns = 3:7,
    method = "numeric",
    palette = c("white", "green"),
    domain = c(0,1)
  )

NHI_rec_tc <- df_NHI |> 
  select(location, nhi_index, max_tc_nhi_0:max_tc_nhi_4) |> 
  gt() |> 
  tab_header(
    title = md("**Max NHI in Transverse Colon vs Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Transverse Colon",
    columns = starts_with("max")
  ) |> 
  cols_label(
    max_tc_nhi_0 = 0,
    max_tc_nhi_1 = 1,
    max_tc_nhi_2 = 2,
    max_tc_nhi_3 = 3,
    max_tc_nhi_4 = 4,
    nhi_index = "NHI"
  )
```

# NHI rectum vs DC
```{r}
NHI_rec_dc_per <- df_NHI |> 
  select(location, nhi_index, percent_max_dc_nhi_0:percent_max_dc_nhi_4) |> 
  gt() |> 
  fmt_percent() |> 
  tab_header(
    title = md("**Max NHI in Descending Colon vs Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Descending Colon",
    columns = starts_with("percent")
  ) |> 
  cols_label(
    percent_max_dc_nhi_0 = 0,
    percent_max_dc_nhi_1 = 1,
    percent_max_dc_nhi_2 = 2,
    percent_max_dc_nhi_3 = 3,
    percent_max_dc_nhi_4 = 4,
    nhi_index = "NHI"
  ) |> 
  data_color(
    columns = 3:7,
    method = "numeric",
    palette = c("white", "green"),
    domain = c(0,1)
  )

NHI_rec_dc <- df_NHI |> 
  select(location, nhi_index, max_dc_nhi_0:max_dc_nhi_4) |> 
  gt() |> 
  tab_header(
    title = md("**Max NHI in Descending Colon vs Rectum**")
  ) |> 
  tab_spanner(
    label = "Max NHI in Descending Colon",
    columns = starts_with("max")
  ) |> 
  cols_label(
    max_dc_nhi_0 = 0,
    max_dc_nhi_1 = 1,
    max_dc_nhi_2 = 2,
    max_dc_nhi_3 = 3,
    max_dc_nhi_4 = 4,
    nhi_index = "NHI"
  )
```

```{r}
NHI_rec_ac_per |> 
  gtsave(filename = "AC_per.png")

NHI_rec_ac |> 
  gtsave(filename = "AC_num.png")

NHI_rec_tc_per |> 
  gtsave(filename = "tc_per.png")

NHI_rec_tc |> 
  gtsave(filename = "tc_num.png")

NHI_rec_dc_per |> 
  gtsave(filename = "dc_per.png")

NHI_rec_dc |> 
  gtsave(filename = "dc_num.png")
```

