---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup}
library(tidyverse)
library(xlsx)
library(DT)
library(gt)
library(webshot2)
```

# Import data from study database .xlsx file

```{r, import xlsx file}
fname <- "FNIH prospective study database excluding follow-up exams.xlsx"
```

```{r}
q1 <- xlsx::read.xlsx2(file = fname, startRow = 3, sheetName = "Worksheet (2)")


q1 <- q1 |> 
  select(MES_Rectum, contains("RHI_max")) |> 
  mutate(
    across(contains("RHI_max"), as.integer)
  ) |> 
  mutate(
    across(contains("MES_Rectum"), as.integer) 
  ) |> 
  drop_na()
  

datatable(q1)
```

# MES in Rectum vs Max NHI

```{r}
df_MES <- read.xlsx2(fname, sheetName = "MES_vs_RHI")
df_MES_re <- df_MES |>
  mutate(
    across(3:26, as.integer)
  ) 
```

select cases where MES_Rectum == 0 vs max RHI in AC

```{r}
df_MES_re[1,3] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_AC <= 3))
df_MES_re[1,4] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_AC > 3) & (q1$RHI_max_AC <= 9))
df_MES_re[1,5] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_AC > 9))

df_MES_re[2,3] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_AC <= 3))
df_MES_re[2,4] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_AC >3) & (q1$RHI_max_AC <= 9))
df_MES_re[2,5] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_AC > 9))

df_MES_re[3,3] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_AC <= 3))
df_MES_re[3,4] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_AC >3) & (q1$RHI_max_AC <= 9))
df_MES_re[3,5] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_AC > 9))
```


select cases where MES_Rectum == 0 vs max RHI in TC

```{r}
df_MES_re[1,6] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_TC <= 3))
df_MES_re[1,7] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_TC > 3) & (q1$RHI_max_TC <= 9))
df_MES_re[1,8] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_TC > 9))

df_MES_re[2,6] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_TC <= 3))
df_MES_re[2,7] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_TC > 3) & (q1$RHI_max_TC <= 9))
df_MES_re[2,8] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_TC > 9))

df_MES_re[3,6] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_TC <= 3))
df_MES_re[3,7] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_TC > 3) & (q1$RHI_max_TC <= 9))
df_MES_re[3,8] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_TC > 9))
```

select cases where MES_Rectum == 0 vs max RHI in DC

```{r}
df_MES_re[1,9] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_DC <= 3))
df_MES_re[1,10] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_DC > 3) & (q1$RHI_max_DC <= 9))
df_MES_re[1,11] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_DC > 9))

df_MES_re[2,9] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_DC <= 3))
df_MES_re[2,10] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_DC > 3) & (q1$RHI_max_DC <= 9))
df_MES_re[2,11] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_DC > 9))

df_MES_re[3,9] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_DC <= 3))
df_MES_re[3,10] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_DC > 3) & (q1$RHI_max_DC <= 9))
df_MES_re[3,11] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_DC > 9))
```

select cases where MES_Rectum == 0 vs max RHI in RE

```{r}
df_MES_re[1,12] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_RE <= 3))
df_MES_re[1,13] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_RE > 3) & (q1$RHI_max_RE <= 9))
df_MES_re[1,14] <- sum((q1$MES_Rectum == 0) & (q1$RHI_max_RE > 9))

df_MES_re[2,12] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_RE <= 3))
df_MES_re[2,13] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_RE > 3) & (q1$RHI_max_RE <= 9))
df_MES_re[2,14] <- sum((q1$MES_Rectum == 1) & (q1$RHI_max_RE > 9))

df_MES_re[3,12] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_RE <= 3))
df_MES_re[3,13] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_RE > 3) & (q1$RHI_max_RE <= 9))
df_MES_re[3,14] <- sum((q1$MES_Rectum > 1) & (q1$RHI_max_RE > 9))
```

calculate percentages

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_ac_rhi..3 = max_ac_rhi..3 / sum(max_ac_rhi..3, max_ac_rhi..9, max_ac_rhi.9)) |> 
  mutate(percent_max_ac_rhi..9 = max_ac_rhi..9 / sum(max_ac_rhi..3, max_ac_rhi..9, max_ac_rhi.9)) |> 
  mutate(percent_max_ac_rhi.9 = max_ac_rhi.9 / sum(max_ac_rhi..3, max_ac_rhi..9, max_ac_rhi.9))
```

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_tc_rhi..3 = max_tc_rhi..3 / sum(max_tc_rhi..3, max_tc_rhi..9, max_tc_rhi.9)) |> 
  mutate(percent_max_tc_rhi..9 = max_tc_rhi..9 / sum(max_tc_rhi..3, max_tc_rhi..9, max_tc_rhi.9)) |> 
  mutate(percent_max_tc_rhi.9 = max_tc_rhi.9 / sum(max_tc_rhi..3, max_tc_rhi..9, max_tc_rhi.9))
```

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_dc_rhi..3 = max_dc_rhi..3 / sum(max_dc_rhi..3, max_dc_rhi..9, max_dc_rhi.9)) |> 
  mutate(percent_max_dc_rhi..9 = max_dc_rhi..9 / sum(max_dc_rhi..3, max_dc_rhi..9, max_dc_rhi.9)) |> 
  mutate(percent_max_dc_rhi.9 = max_dc_rhi.9 / sum(max_dc_rhi..3, max_dc_rhi..9, max_dc_rhi.9))
```

```{r}
df_MES_re <- df_MES_re |> 
  rowwise() |> 
  mutate(percent_max_re_rhi..3 = max_re_rhi..3 / sum(max_re_rhi..3, max_re_rhi..9, max_re_rhi.9)) |> 
  mutate(percent_max_re_rhi..9 = max_re_rhi..9 / sum(max_re_rhi..3, max_re_rhi..9, max_re_rhi.9)) |> 
  mutate(percent_max_re_rhi.9 = max_re_rhi.9 / sum(max_re_rhi..3, max_re_rhi..9, max_re_rhi.9))
```

Format values as xx.x% (n)

```{r}
df_MES_re <- df_MES_re |> 
  mutate(max_ac_rhi..3_f = paste0(format(round(percent_max_ac_rhi..3 * 100, 1), nsmall = 1), "%\n(", max_ac_rhi..3, ")")) |> 
  mutate(max_ac_rhi..9_f = paste0(format(round(percent_max_ac_rhi..9 * 100, 1), nsmall = 1), "%\n(", max_ac_rhi..9, ")")) |> 
  mutate(max_ac_rhi.9_f = paste0(format(round(percent_max_ac_rhi.9 * 100, 1), nsmall = 1), "%\n(", max_ac_rhi.9, ")")) |> 
  mutate(max_tc_rhi..3_f = paste0(format(round(percent_max_tc_rhi..3 * 100, 1), nsmall = 1), "%\n(", max_tc_rhi..3, ")")) |> 
  mutate(max_tc_rhi..9_f = paste0(format(round(percent_max_tc_rhi..9 * 100, 1), nsmall = 1), "%\n(", max_tc_rhi..9, ")")) |> 
  mutate(max_tc_rhi.9_f = paste0(format(round(percent_max_tc_rhi.9 * 100, 1), nsmall = 1), "%\n(", max_tc_rhi.9, ")")) |> 
  mutate(max_dc_rhi..3_f = paste0(format(round(percent_max_dc_rhi..3 * 100, 1), nsmall = 1), "%\n(", max_dc_rhi..3, ")")) |> 
  mutate(max_dc_rhi..9_f = paste0(format(round(percent_max_dc_rhi..9 * 100, 1), nsmall = 1), "%\n(", max_dc_rhi..9, ")")) |> 
  mutate(max_dc_rhi.9_f = paste0(format(round(percent_max_dc_rhi.9 * 100, 1), nsmall = 1), "%\n(", max_dc_rhi.9, ")")) |> 
  mutate(max_re_rhi..3_f = paste0(format(round(percent_max_re_rhi..3 * 100, 1), nsmall = 1), "%\n(", max_re_rhi..3, ")")) |> 
  mutate(max_re_rhi..9_f = paste0(format(round(percent_max_re_rhi..9 * 100, 1), nsmall = 1), "%\n(", max_re_rhi..9, ")")) |> 
  mutate(max_re_rhi.9_f = paste0(format(round(percent_max_re_rhi.9 * 100, 1), nsmall = 1), "%\n(", max_re_rhi.9, ")"))
```

## MES rectum vs RHI AC

```{r}
MES_r_RHI_a <- df_MES_re |> 
  select(location, mes_index, max_ac_rhi..3_f:max_ac_rhi.9_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max RHI in Ascending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max RHI in Ascending Colon",
    columns = starts_with("max_ac")
  ) |> 
  cols_label(
    max_ac_rhi..3_f = c("\u2264 3"),
    max_ac_rhi..9_f = c("\u2264 9"),
    max_ac_rhi.9_f = "> 9",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_RHI_a
```

## MES rectum vs RHI TC

```{r}
MES_r_RHI_t <- df_MES_re |> 
  select(location, mes_index, max_tc_rhi..3_f:max_tc_rhi.9_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max RHI in Transverse Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max RHI in Transverse Colon",
    columns = starts_with("max_tc")
  ) |> 
  cols_label(
    max_tc_rhi..3_f = c("\u2264 3"),
    max_tc_rhi..9_f = c("\u2264 9"),
    max_tc_rhi.9_f = "> 9",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_RHI_t
```

## MES rectum vs RHI DC

```{r}
MES_r_RHI_d <- df_MES_re |> 
  select(location, mes_index, max_dc_rhi..3_f:max_dc_rhi.9_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max RHI in Descending Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max RHI in Descending Colon",
    columns = starts_with("max_dc")
  ) |> 
  cols_label(
    max_dc_rhi..3_f = c("\u2264 3"),
    max_dc_rhi..9_f = c("\u2264 9"),
    max_dc_rhi.9_f = "> 9",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_RHI_d
```

## MES rectum vs RHI RE

```{r}
MES_r_RHI_r <- df_MES_re |> 
  select(location, mes_index, max_re_rhi..3_f:max_re_rhi.9_f) |> 
  gt() |> 
  fmt_percent(
    decimals = 1
  ) |> 
  tab_header(
    title = md("**Max RHI in Rectum Colon vs MES in Rectum**")
  ) |> 
  tab_spanner(
    label = "Max RHI in Rectum Colon",
    columns = starts_with("max_re")
  ) |> 
  cols_label(
    max_re_rhi..3_f = c("\u2264 3"),
    max_re_rhi..9_f = c("\u2264 9"),
    max_re_rhi.9_f = "> 9",
    mes_index = "MES"
#  ) |> 
#  data_color(
#    columns = 3:7,
#    method = "numeric",
#    palette = c("blue", "red"),
#    domain = c(0,1)
  )

MES_r_RHI_r
```

```{r}
q1 |> select(contains("RHI_max"))
```


```{r, eval= FALSE}
MES_r_RHI_a |> 
  gtsave(filename = "output_tables/mes_r_rhi_a.png")

MES_r_RHI_t |> 
  gtsave(filename = "output_tables/mes_r_rhi_t.png")

MES_r_RHI_d |> 
  gtsave(filename = "output_tables/mes_r_rhi_d.png")

MES_r_RHI_r |> 
  gtsave(filename = "output_tables/mes_r_rhi_r.png")
```

```{r, eval= FALSE}
MES_r_RHI_a |> 
  gtsave(filename = "output_tables/mes_r_rhi_a.docx")

MES_r_RHI_t |> 
  gtsave(filename = "output_tables/mes_r_rhi_t.docx")

MES_r_RHI_d |> 
  gtsave(filename = "output_tables/mes_r_rhi_d.docx")

MES_r_RHI_r |> 
  gtsave(filename = "output_tables/mes_r_rhi_r.docx")
```